### 2017-06-19 Doc/classicthesis/Chapters/Chapter0A.tex
ieee

The second image shows the issuance of the credential, divided in the three REST calls needed during the delegation. If we recall Idemix's issuance protocol, the User performed, during his first step, an exponentiation with his secret key and a ZKP, which can be identified by the \texttt{COMMITMENT} and \texttt{ISSUANCE RESPONSE} commands. During the second step, the User only has to verify the Issuer's ZKP and store the credential if the signature is valid. Because the P2ABC Engine can perform Verification of ZKP without the need of secret keys stored in the smart card, the APDU Commands in this phase are only for storing the credential information inside the IoT smart card's BLOB\footnote{(\textbf{B}inary \textbf{L}arge \textbf{Ob}jects} database, with the \texttt{STORE BLOB} instruction.

@@

\chapter{Attached code structure}\label{ch:code}

>>>>

The second image shows the issuance of the credential, divided in the three REST calls needed during the delegation. If we recall Idemix's issuance protocol, the User performed, during his first step, an exponentiation with his secret key and a ZKP, which can be identified by the \texttt{COMMITMENT} and \texttt{ISSUANCE RESPONSE} commands. During the second step, the User only has to verify the Issuer's ZKP and store the credential if the signature is valid. Because the P2ABC Engine can perform Verification of ZKP without the need of secret keys stored in the smart card, the APDU Commands in this phase are only for storing the credential information inside the IoT smart card's BLOB\footnote{\textbf{B}inary \textbf{L}arge \textbf{Ob}jects} database, with the \texttt{STORE BLOB} instruction.

@@

\chapter{Paper proposal for JCR Magazine}\label{ch:JCR}

a

\chapter{Project's code structure}\label{ch:code}

### 2017-06-19 Doc/classicthesis/Chapters/Design.tex
ieee

>>>>

\section{Design and implementation conclusions}

During this design and implementation process we had to study multiple technologies, including the ones mentioned in the state of the art, regarding Idemix, and those related to the IoT, we studied many systems (e.g. Contiki, Arduino) and hardware (e.g. MSP430, ESP8266), and after this, we had to take many decisions during development.

The design is open in those aspects that depend on each specific project's requisites, and closed on the aspects involving the P2ABCE's core logic.

However, the PoC had to make more concessions when implementing the cryptographic and modular arithmetic logic. But those are parts of the code that are more prone to be changed when developing for a new system. The core logic of the PoC is preserved as it is in every system and device.

Even with the many points of future work left, we think we achieved the most extensible solution for Idemix+IoT at the time, our main objective of the project.

### 2017-06-19 Doc/classicthesis/Chapters/Introduction.tex
ieee

The goal of this project is to integrate Idemix with the IoT. It will be done using the ABC4Trust's \acf{P2ABCE}, a framework that defines a common architecture, policy language and data artifacts for an attribute based ecosystem, cryptographically based on either IBM's Idemix or Microsoft's U-Prove \footnote{P2ABCEngine \url{https://github.com/p2abcengine/p2abcengine}}. This gives us a standardized language to exchange Idemix's messages between IoT devices and any other P2ABCE actor.

>>>>

As part of IBM's academic grant for \textit{Privacy Preserving Identity Management applied to IoT}, the goal of this project is to integrate Idemix with the IoT. It will be done using ABC4Trust's \acf{P2ABCE}, a framework that defines a common architecture, policy language and data artifacts for an attribute based ecosystem, cryptographically based on either IBM's Idemix or Microsoft's U-Prove \footnote{P2ABCEngine \url{https://github.com/p2abcengine/p2abcengine}}. This gives us a standardized language to exchange Idemix's messages between IoT devices and any other P2ABCE actor.

### 2017-06-19 Doc/classicthesis/Chapters/Validation.tex
ieee

>>>>

\section{Validation conclusions}

Below \autoref{totaltime} sums up the time in seconds used in each step of the test for the Omega2 and Raspberry Pi 3 setup.

The first step, \textit{System Setup} is done only once when the system is being deployed, and the \textit{IoT Smart Card Setup} only once per device.

Because a device can have more than one credential, the Issuance step is significant when we issue multiple credentials over the device's lifetime. We recall that our tests used a credential with five attributes and key sizes of 1024 bits.

Finally, the Proving step is expected to be the most performed calculation by the IoT device. The fact that it lasts over half a minute implies that we should not use this PoC for \textit{real-time} applications yet, usually used in critical secure systems. Nevertheless, for many other IoT applications, the fact this operation can be performed multiple times per hour, presents an useful tool for privacy, e.g. the thermostat system mentioned in the smart building, which can pool data from the sensors every few minutes.

\begin{table}[!ht]
	\begin{center}
		\begin{tabular}{|r|r|r|r|}
		\hline
		System & IoT Smart  & Issue  & Prove Presen-\\
		Setup & Card Setup & credential & tation Policy\\ \hline
		3.77 s & 19.19 s & 36.48 s & 32.84 s \\ \hline
	\end{tabular}
	\end{center}
\caption{Total time spent for each step in the Omega2+RPi3 setup.}
\label{totaltime}
\end{table}

### 2017-06-19 Doc/classicthesis/FrontBackmatter/Abstract.tex
ieee

As part of IBM's academic grant for \textit{Privacy Preserving Identity Management applied to IoT}, we designed a solution to integrate IBM's Identity Mixer into the IoT ecosystem, in a privacy-preserving fashion thanks to the use of Zero-Knowledge Proof cryptography. To validate our design, we implemented a functional Proof of Concept written in C for IoT devices. The applications of such solution promise to improve both the security and privacy of IoT, which in recent years have proved to be compromised.

>>>>

In this paper we design a solution to integrate IBM's Identity Mixer into the IoT ecosystem, integrating its privacy-preserving capabilities thanks to the use of Zero-Knowledge Proof cryptography. To validate our design, we implemented a functional Proof of Concept written in C for IoT devices. The applications of such solution promise to improve both the security and privacy of IoT, which in recent years have proved to be compromised.
